Implementing XBF: An Efficient Self-Describing Binary Format

### 2023-08-08 docs/paper.tex
Update paper

\section{Methodology and Implementation}

>>>>

\section{Format Design}

\section{Implementation}

\section{Evaluation}

XBF was evaluated against a number of other self-describing data interchange formats.

\begin{IEEEitemize}
	\item CSV (Comma Separated Values) \cite{csv_spec}\cite{csv_parser}
	\item MessagePack \cite{msgpack_spec}\cite{msgpack_parser}
	\item CBOR (Concise Binary Object Representation) \cite{cbor_spec}\cite{cbor_parser}
	\item JSON \cite{json_parser}
	\item XML \cite{xml_parser}
\end{IEEEitemize}

The primary goal of the test was to measure how many bytes a particular format required to transmit a given set of data, with the secondary objective being to measure the timed performance of the format. The data\cite{sony_stock_data} was a year of.
